
% !TEX program = pdflatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS

%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.45in,top=0.5in,right=0.45in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% [set line spacing
\renewcommand{\baselinestretch}{0.8} % normal line spacing
% [ url links
\usepackage{hyperref}
% ]

% [
\usepackage{etaremune} % reverse enumeration
% ]

\usepackage[parfill]{parskip}
\setlength{\parskip}{1.5pt} % line spacing for new lines

% \setlength{\parindent}{} % paragraph indentation



\name{Ojasv Kamal} % Your name
% \address{The University of Hong Kong, China}
\address{
% New York University \\ 
\href{mailto:kamalojasv2000@gmail.com}{kamalojasv2000@gmail.com} \\ \url{https://github.com/kamalojasv181} \\ (+91) 9215650602} % Line 3
% \address{Department of Computer Science} % Line 1

\begin{document}
% Examples to Learn from: https://yardi.people.si.umich.edu/Schoenebeck_CV.pdf
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Education}
\vspace{0.3cm}

{\bf Indian Institute of Technology Kharagpur } \hfill { Kharagpur, India} 
\\ B.Tech M.Tech Dual Degree, Mechanical Engineering; CGPA: 8.85/10 \hfill { \em  July 2018 – Present}
\vspace{0.1cm}
\\
{\bf Sukriti World School } \hfill { New Delhi, India} 
\\ All India Senior School Certificate Examination (AISSCE); Percentage: 92.8/100 \hfill { \em  2017 – 2018}
\vspace{0.1cm}
\\
{\bf Scholars Rosary Senior Secondary School } \hfill { Rohtak, India} 
\\ All India Secondary School Examination (AISSE); CGPA: 10/10 \hfill { \em  2015 – 2016}

\end{rSection}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications} \itemsep -2pt
    \begin{etaremune}[start  = 3] % Update when you add a publication
       \item \textbf{When to Make Exceptions: Exploring Language Models as Accounts of Human Moral Judgment
       }
       
       Zhijing Jin, Sydney Levine, Fernando Gonzalez, \textbf{Ojasv Kamal}, Maarten Sap, Mrinmaya Sachan, Rada Mihalcea, Josh Tenenbaum, Bernhard Schölkopf.
       
        \emph{In Proceedings of the Advances in Neural Information Processing Systems 35} (NeurIPS 2022). \\Available at 
        \url{https://arxiv.org/abs/2210.01478}.
    
       \item \textbf{Adversities are all you need: Classification of self-reported breast cancer posts on Twitter using Adversarial Fine-tuning.}
       
       Adarsh Kumar$^*$, \textbf{Ojasv Kamal$^*$}, Susmita Mazumdar$^*$ (Equal Contribution). 
       
       \emph{In Proceedings of the Sixth Social Media Mining for Health (SMM4H) Workshop and Shared Task NAACL 2021}. Available at \url{https://aclanthology.org/2021.smm4h-1.22/}.
       
       \item \textbf{Hostility detection in Hindi leveraging pre-trained language models.}
       
       \textbf{Ojasv Kamal$^*$}, Adarsh Kumar$^*$ (equal contribution), Tejas Vaidhya. 
       
       \emph{International Workshop on Combating Online Hostile Posts in Regional Languages during Emergency Situation, AAAI 2021}. Available at \url{https://link.springer.com/chapter/10.1007/978-3-030-73696-5_20}
       

      
    \end{etaremune}

    
    \end{rSection}

\begin{rSection}{Research Experience}

{\bf Analysing Meta-Contrastive Learning for Few-Shot Slot Filling} \hfill { } 
\\ \textit{NUS, Web Information Retrieval / Natural Language Processing Group, with Prof. Min-Yen Kan} \hfill { \em }
\begin{itemize}
\item Interpreted the complex process of meta-learning by studying the two levels of base and meta learning separately.
\item Quantified the effect of using contrastive learning as the base learning algorithm for few-shot slot filling.
\item Performed 42 abilation tests on 7 dataset domains to study the effect of removing each domain.
\item Correlated the performance drop with 19 out-of-domain metrics representing text properties to interpret the role of contrastive learning in meta learning.
\end{itemize}


\end{rSection}



%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
{\bf Amazon AI,} \textit{Research Intern} \hfill {July 2019 - present}

{\bf MIT Media Lab,} \textit{Undergraduate Researcher} \hfill {Sept 2017 - Feb 2018}

{\bf Shanghai Jiao Tong University,} \textit{Undergraduate Researcher} \hfill {July 2017 - Aug 2017}

{\bf Vega Global Japan,} \textit{Assistant to Country Manager} \hfill {Jan 2017 - Feb 2017}

% \begin{itemize}
  
%   \item Launched and maintained the company intranet using Apache and WordPress
%   \item Designed and implemented a data pipeline between Google API and Pipeliner CRM API
% \end{itemize}

{\bf Eastern International Academy,} \textit{International Teacher} \hfill {July 2016 - Aug 2016}
\end{rSection}

\begin{rSection}{Awards \& Honors} \itemsep -2pt
\begin{enumerate}
  \item \textbf{First Class Honours}, The University of Hong Kong, 2019.
  \item \textbf{HKU Foundation Entrance Scholarship}, The University of Hong Kong, 2015 - 2019.
  \\Top 3 among 19,000 students in the National College Examination in Shanghai, China. \\Covered 4 years of tuition fees for undergraduate study.
  \item \textbf{Hong Kong Government Scholarship Fund}, Hong Kong, 2017 - 2019.
  \item \textbf{Hong Kong, China - Asia-Pacific Economic Cooperation Scholarship}, Hong Kong, 2018 - 2019.
  \item \textbf{Rosita King Ho Scholarship} for Academic Excellence in \textbf{Exchange to National Taiwan University} (GPA: 3.86/4.3), Taiwan, 2017.
  \item \textbf{Hong Kong Government Reach-Out Award} for Volunteer Work in Phnom Penh, Cambodia, 2016.
  \item \textbf{Dean's List}, The University of Hong Kong, 2015, 2016.
\end{enumerate}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Invited Talks}


{\bf Mar 11, 2020.  ``Language Adversarial Attack against BERT.''} \href{https://lit.eecs.umich.edu/}{Invited Talk at University of Michigan Language and Information Technologies Lab}, United States. 

{\bf Mar 2, 2020. ``The Power of Unsupervised Text Generation -- Taking Adversarial Attack as an Example.''} Invited Talk at \href{https://is.mpg.de/}{Max Planck Institute for Intelligent Systems}, Germany. 

{\bf Feb 12, 2020. ``New Advances in NLP Adversarial Attack.''}  Invited Talk by \href{https://syncedreview.com/}{\emph SyncedTech}, one of the top media on Artificial Intelligence. The talk hit a record high of 3,697 listeners.

\end{rSection}


\begin{rSection}{Professional Service}

\textbf{Reviewer}, the 2020 Annual Conference of the Association for Computational Linguistics. ACL 2020. 


\end{rSection}

\begin{rSection}{Advising \& Mentoring}
\textbf{Master Students}
\begin{itemize}
    \item Xiaoyu Xing, 2020. Master in Computer Science at Fudan University.
\end{itemize}


\textbf{Undergraduate Students}

\begin{itemize}
    \item Yongyi Yang, 2019-2020. Undergraduate in Computer Science at Fudan University.
    \item Yuchun Dai, 2020. Undergraduate in Computer Science at Fudan University.
\end{itemize}


\end{rSection}

\begin{rSection}{Selected Press}

\textit{``Hey Alexa, sorry I fooled you.''} MIT News, 2020. http://news.mit.edu/2020/hey-alexa-sorry-i-fooled-you-0207.

\textit{``TextFooler Generates Adversarial Text to Strengthen Natural Language Models.''} ACM TechNews, 2020. https://technews.acm.org/archives.cfm?fo=2020-02-feb/feb-07-2020.html

\end{rSection}


\begin{rSection}{Community Contribution} \itemsep -2pt
\begin{enumerate}
    \item \textbf{Member of Effective Altruism} in Shanghai, China, 2019 - present.
  \item \textbf{Volunteer Kids' Church Organizer} at Cambridge Community Fellowship Church, MA, US, 2018.
  
  \item \textbf{Volunteer Teacher} in Phnom Penh, Cambodia, 2016.
  \\ Rewarded \textit{Hong Kong Government Reach-Out Award 2016}.
  
  \item \textbf{Volunteer Kids' Church Helper} at Saint Peter's Church, Shanghai, China, 2015.
  \item \textbf{Volunteer Teacher} at Three-Leaf Clover Kindergarten for Autistic Children, Shanghai, China, 2014.
  
  
\end{enumerate}

\end{rSection}

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages &  English, Mandarin, German, Japanese, Cantonese, Shanghainese, Classical Chinese  \\
Programming Skills &  Python, Javascript, NodeJS, PHP, CSS, HTML, Excel VBA, Java, C/C++, MySQL \\
Design Skills & Photoshop, Unity, WordPress, Prezi,
Microsoft Suite (Word, Excel, Powerpoint) \\
Technologies & Pytorch, TensorFlow, Keras \\
% Interests  & Biking, Hiking, Yoga, Meditation, Archaeology and History \\

\end{tabular}

\end{rSection}



\end{document}